partial: An R Package for Creating Partial Dependence Plots

### 2016-08-10 manuscript/greenwell.tex
minor edits

The benefit of using \code{partial} is threefold: (1) it is a generic function that can be used for various types of model fits (not just random forests), (2) it will allow for any number of predictors to be used, and (3) it can utilize any of the parallel backends supported by the \CRANpkg{foreach} package \citep{foreach-pkg}; we discuss parallel execution in a later section. For example, the following code chunk uses a multivariate adaptive regression splines (MARS) model \citep{friedman-1991-mars} to assess the joint effect of \code{lstat} and \code{rm} on \code{cmedv}. The results, which make use of various \code{plotPartial} options, are displayed in Figure~\ref{fig:pd_lstat_rm}.
\begin{example}
library(earth)  # for fitting MARS models
boston.mars <- earth(cmedv ~ ., data = boston, degree = 3)
pd.lstat.rm <- partial(boston.mars, pred.var = c("lstat", "rm"))
plotPartial(pd.lstat.rm)
plotPartial(pd.lstat.rm, col.regions = colorRampPalette(c("white", "blue")))
plotPartial(pd.lstat.rm, contour = FALSE, zlab = "cmedv", drape = TRUE,
            colorkey = TRUE, screen = list(z = -20, x = -60))
\end{example}
Note that the default color map for contour plots is the Matplotlib "viridis" color map provided through the \CRANpkg{viridis} package \citep{viridis-pkg}.

>>>>

The benefit of using \code{partial} is threefold: (1) it is a generic function that can be used for various types of model fits (not just random forests), (2) it will allow for any number of predictors to be used, and (3) it can utilize any of the parallel backends supported by the \CRANpkg{foreach} package \citep{foreach-pkg}; we discuss parallel execution in a later section. For example, the following code chunk uses a multivariate adaptive regression splines (MARS) model \citep{friedman-1991-mars} to assess the joint effect of \code{lstat} and \code{rm} on \code{cmedv}. The results, which make use of various \code{plotPartial} options, are displayed in Figure~\ref{fig:pd_lstat_rm}.
\begin{example}
library(earth)  # for fitting MARS models
boston.mars <- earth(cmedv ~ ., data = boston, degree = 3)
pd.lstat.rm <- partial(boston.mars, pred.var = c("lstat", "rm"))
plotPartial(pd.lstat.rm)
plotPartial(pd.lstat.rm, col.regions = colorRampPalette(c("red", "white", "blue")))
plotPartial(pd.lstat.rm, contour = FALSE, zlab = "cmedv", drape = TRUE,
            colorkey = TRUE, screen = list(z = -20, x = -60))
\end{example}
Note that the default color map for contour plots is the Matplotlib "viridis" color map provided through the \CRANpkg{viridis} package \citep{viridis-pkg}.
